---
title: '**Supplementary Figures**'
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: null
  latex_engine: pdflatex
  html_document:
    df_print: paged
---

# Increased resilience and regime-shift reversal through repeat mass coral bleaching

\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 0
```

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS1.pdf"); i = i + 1
```

**Fig. S`r i`. Benthic cover (%) from 1994-2022 at each reef for macroalgae at recovering reefs (a) and hard coral at shifted reefs (b).** Points are the mean benthic cover across sites (± 2 * standard error), and grey lines are site-level cover values. Dashed line is the mean pre-bleaching benthic cover in 1994.


```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureS2.pdf"); i = i + 1
```

**Fig. S`r i`. Euclidean distance of recovering (blue) and regime-shifted (red) reefs from 1994-2022.** Points are mean Euclidean distance among all reefs in each survey year shown against (a) hard coral cover (%) and (b) macroalgae cover (%), connected through time with lines.
